---
Title : "An entry to the house prices competition."
Author : "Oleksandr Sorochynskyi"
---

This is my entry to the following competition :
https://www.kaggle.com/competitions/house-prices-advanced-regression-techniques/code

Thoughout this document I refer to the data as `boston`, I only found out data
is not from Boston much later :o


# Data import

```{r}
options(width = 150)

library(tidyverse)

read_boston <- . %>% read_csv(
    col_types = cols(
        Id = col_double(),
        MSSubClass = col_double(),
        MSZoning = col_character(),
        LotFrontage = col_double(),
        LotArea = col_double(),
        Street = col_character(),
        Alley = col_character(),
        LotShape = col_character(),
        LandContour = col_character(),
        Utilities = col_character(),
        LotConfig = col_character(),
        LandSlope = col_character(),
        Neighborhood = col_character(),
        Condition1 = col_character(),
        Condition2 = col_character(),
        BldgType = col_character(),
        HouseStyle = col_character(),
        OverallQual = col_double(),
        OverallCond = col_double(),
        YearBuilt = col_double(),
        YearRemodAdd = col_double(),
        RoofStyle = col_character(),
        RoofMatl = col_character(),
        Exterior1st = col_character(),
        Exterior2nd = col_character(),
        MasVnrType = col_character(),
        MasVnrArea = col_double(),
        ExterQual = col_character(),
        ExterCond = col_character(),
        Foundation = col_character(),
        BsmtQual = col_character(),
        BsmtCond = col_character(),
        BsmtExposure = col_character(),
        BsmtFinType1 = col_character(),
        BsmtFinSF1 = col_double(),
        BsmtFinType2 = col_character(),
        BsmtFinSF2 = col_double(),
        BsmtUnfSF = col_double(),
        TotalBsmtSF = col_double(),
        Heating = col_character(),
        HeatingQC = col_character(),
        CentralAir = col_character(),
        Electrical = col_character(),
        `1stFlrSF` = col_double(),
        `2ndFlrSF` = col_double(),
        LowQualFinSF = col_double(),
        GrLivArea = col_double(),
        BsmtFullBath = col_double(),
        BsmtHalfBath = col_double(),
        FullBath = col_double(),
        HalfBath = col_double(),
        BedroomAbvGr = col_double(),
        KitchenAbvGr = col_double(),
        KitchenQual = col_character(),
        TotRmsAbvGrd = col_double(),
        Functional = col_character(),
        Fireplaces = col_double(),
        FireplaceQu = col_character(),
        GarageType = col_character(),
        GarageYrBlt = col_double(),
        GarageFinish = col_character(),
        GarageCars = col_double(),
        GarageArea = col_double(),
        GarageQual = col_character(),
        GarageCond = col_character(),
        PavedDrive = col_character(),
        WoodDeckSF = col_double(),
        OpenPorchSF = col_double(),
        EnclosedPorch = col_double(),
        `3SsnPorch` = col_double(),
        ScreenPorch = col_double(),
        PoolArea = col_double(),
        PoolQC = col_character(),
        Fence = col_character(),
        MiscFeature = col_character(),
        MiscVal = col_double(),
        MoSold = col_double(),
        YrSold = col_double(),
        SaleType = col_character(),
        SaleCondition = col_character(),
        SalePrice = col_double()
    )
)
mutate_boston <- . %>% mutate(
        GarageType = GarageType %>%
            replace_na("None") %>%
            fct_relevel("None", after = 0),
        Alley = Alley %>%
            replace_na("None") %>%
            fct_relevel("None", after = 0),
        HeatingQC = case_when(
            HeatingQC == "Ex" ~ 5,
            HeatingQC == "Gd" ~ 4,
            HeatingQC == "TA" ~ 3,
            HeatingQC == "Fa" ~ 2,
            HeatingQC == "Po" ~ 1,
        ),
        Heating = fct_lump_n(Heating, 1),
        outlier = SalePrice > 6e5 | `1stFlrSF` > 2500 |
            TotalBsmtSF > 3000 | LotArea > 50e3
    )

data_zip <- "data/house-prices-advanced-regression-techniques.zip"
boston_raw <- unz(
    data_zip,
    "train.csv"
) %>%
    read_boston()

boston <- boston_raw %>%
    mutate_boston()
   
set.seed(1)
test_set <- sample.int(nrow(boston), size = floor(0.3 * nrow(boston)))
test_test_set <- sample(test_set, size = floor(length(test_set) / 3))
test_set <- test_set[!test_set %in% test_test_set]
train_set <- seq_len(nrow(boston))[-c(test_set, test_test_set)]
boston_test <- slice(boston, test_set)
boston_test_test <- slice(boston, test_test_set)
boston <- slice(boston, train_set)
```

Getting an overall idea of the columns/data types

```{r}
boston %>%
    mutate(across(where(is.character), as.factor)) %>%
    summary()
```


# GLM 

To get a baseline I turn to linear model. Initially, all variables were
included some were then removed when if I had a reason to do so, e.g. if they
redundant or almost constant. 

```{r}
library(splines)
m1 <- glm(
    SalePrice ~ MSSubClass + MSZoning +
        ns(LotArea, 5) + LotShape + LandContour +
        LotConfig + LandSlope + Neighborhood + Condition1 + Condition2 +
        BldgType + HouseStyle + ns(OverallQual, 5) + ns(OverallCond, 3) +
        ns(YearBuilt, 5) +
        YearRemodAdd + RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + ExterCond + Foundation + BsmtFinSF1 + BsmtFinSF2 +
        BsmtUnfSF + TotalBsmtSF + Heating + HeatingQC + CentralAir +
        `1stFlrSF` + `2ndFlrSF` + LowQualFinSF +
        ns(GrLivArea, 5) + BsmtFullBath +
        BsmtHalfBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageType +
        GarageCars + ns(GarageArea, 5) +
        PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + ns(MoSold, 5) +
        YrSold + SaleType + SaleCondition + Alley,
    Gamma(link = log),
    data = boston,
    subset = !outlier
)

summary(m1)
```

First I note that overall the performance seems to be quite good, with a large
majority of the deviance being axplained away.

Other thant that I do note that ther're is perfect dependance beween certain
variables.

```{r}
cmat <- alias(m1)
cmat$Complete[, colSums(cmat$Complete) > 0]
```

Even on the test set the performance remains quite good.

Errors aren't quite as nice as I would have liked, I suspect we can do
better with some non-linearities.

```{r}
test_res <- boston_test %>%
    filter(!outlier) %>%
    mutate(
        SalePrice_pred = predict(m1, ., type = "response"),
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred
    )

1 - var(test_res$err, na.rm = TRUE) / var(test_res$err_base)
test_res$err %>% sd()
test_res$err_base %>% sd()
test_res$err %>% summary()
test_res$err_base %>% summary()

# Mean err plot
test_res %>%
    ggplot() +
    aes(x = err) +
    geom_histogram() +
    geom_vline(xintercept = 0)

# Mean err plot
test_res %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

# err sd plot
test_res %>%
    ggplot() +
    aes(y = sqrt(abs(err)), x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)
```

A quick comparaison of results relative to outliers
```{r}
m1_with_out <- glm(
    SalePrice ~ MSSubClass + MSZoning +
        ns(LotArea, 5) + LotShape + LandContour +
        LotConfig + LandSlope + Neighborhood + Condition1 + Condition2 +
        BldgType + HouseStyle + ns(OverallQual, 5) + ns(OverallCond, 3) +
        ns(YearBuilt, 5) +
        YearRemodAdd + RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + ExterCond + Foundation + BsmtFinSF1 + BsmtFinSF2 +
        BsmtUnfSF + TotalBsmtSF + Heating + HeatingQC + CentralAir +
        `1stFlrSF` + `2ndFlrSF` + LowQualFinSF +
        ns(GrLivArea, 5) + BsmtFullBath +
        BsmtHalfBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageType +
        GarageCars + ns(GarageArea, 5) +
        PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + ns(MoSold, 5) +
        YrSold + SaleType + SaleCondition + Alley,
    Gamma(link = log),
    data = boston
)
as_tibble(cbind(noout = coef(m1), out = coef(m1_with_out)), rownames = "vars") %>%
    mutate(diff = out - noout) %>%
    arrange(desc(abs(diff)))

```
THe first step, however is to determine which variables actually matter.



# Lasso

For glmnet I need to define a matrix, having a bit more control I define xlevels
in such a way as to avoid the problem with "new level in test data".

```{r}
library(glmnet)

boston_all <- bind_rows(
    train = boston,
    test = boston_test,
    test_test = boston_test_test,
    .id = "set"
)

xlevels <- boston_all %>%
    keep(~ all(is.character(.))) %>%
    map(unique)

mf <- model.frame(
    SalePrice ~ MSSubClass + MSZoning +
        ns(LotArea, 5) + LotShape + LandContour +
        LotConfig + LandSlope + Neighborhood + Condition1 + Condition2 +
        BldgType + HouseStyle + ns(OverallQual, 5) + ns(OverallCond, 3) +
        ns(YearBuilt, 5) +
        YearRemodAdd + RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + ExterCond + Foundation + BsmtFinSF1 + BsmtFinSF2 +
        BsmtUnfSF + TotalBsmtSF + Heating + HeatingQC + CentralAir +
        `1stFlrSF` + `2ndFlrSF` + LowQualFinSF +
        ns(GrLivArea, 5) + BsmtFullBath +
        BsmtHalfBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageType +
        GarageCars + ns(GarageArea, 5) +
        PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + ns(MoSold, 5) +
        YrSold + SaleType + SaleCondition + Alley,
    data = boston_all,
    xlev = xlevels
)

boston_x <- model.matrix(mf, data = boston_all, xlev = xlevels)
boston_y <- model.response(mf)

m2 <- cv.glmnet(
    x = boston_x[boston_all$set == "train", ],
    y = boston_y[boston_all$set == "train"],
    # Causes convergence problems, but results are essentially the same
    # family =  Gamma(link = log)
)
```

The performance bombed. The performance on the train set is good, but as soon
as I move the test set it bombs. Even setting lambda = 0 does not result in
a reasonable result. This suggests to me that something fishy is going on,
with the matrix ? I couldn't quite figuire out what was up but converting the
whole dataset into a model.matrix at the same time does seem to do the trick.

The performance is now reasonable, but is still below our baseline  with the
model above. Let us see how test performance changes as a function of lambda.

```{R}
plot(m2)
test_res2 <- tibble(
    SalePrice = boston_y[boston_all$set == "test"],
    SalePrice_pred = predict(
        m2,
        boston_x[boston_all$set == "test", ],
        s = "lambda.min",
        type = "response"
    ),
    err_base = SalePrice - mean(boston$SalePrice),
    err = SalePrice - SalePrice_pred
)

1 - var(test_res2$err) / var(test_res2$err_base)
```

Indeed it appears that for all lambdas the performance is worse. This is strange
given that the non-penalized model should be equivalent to the linear model.

```{r}
test_res2_bis <- tibble(
    lambda = c(m2$lambda, 0),
    y = list(boston_y[boston_all$set == "test"]),
    y_hat = predict(
        m2,
        boston_x[boston_all$set == "test", ],
        s = lambda,
        type = "response"
    ) %>%
        apply(2, function(x) list(x)) %>%
        map(1),
    err = map2(y, y_hat, `-`),
    err_base = map(y, ~ . - mean(boston_y[boston_all$set == "train"])),
    rsq = map2_dbl(err, err_base, ~ 1 - var(.x) / var(.y))
)

test_res2_bis %>%
    ggplot() +
    aes(x = log(lambda), y = rsq) +
    geom_point() +
    expand_limits(x = 1, y = 1)
```


# From a single tree

```{r}
library(rpart)

m3 <- rpart(
    SalePrice ~ MSSubClass + MSZoning +
        LotArea + LotShape + LandContour +
        LotConfig + LandSlope + Neighborhood + Condition1 + Condition2 +
        BldgType + HouseStyle + OverallQual + OverallCond +
        YearBuilt +
        YearRemodAdd + RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + ExterCond + Foundation + BsmtFinSF1 + BsmtFinSF2 +
        BsmtUnfSF + TotalBsmtSF + Heating + HeatingQC + CentralAir +
        `1stFlrSF` + `2ndFlrSF` + LowQualFinSF +
        GrLivArea + BsmtFullBath +
        BsmtHalfBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageType +
        GarageCars + GarageArea +
        PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + MoSold +
        YrSold + SaleType + SaleCondition + Alley,
    data = boston
)


test_res3 <- boston_test %>%
    filter(!HeatingQC %in% "Po") %>%
    mutate(
        SalePrice_pred = predict(m3, .),
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred
    )


1 - var(test_res3$err, na.rm = TRUE) / var(test_res3$err_base)
```

# To a forest

```{r}
library(ranger)

m4 <- ranger(
    SalePrice ~ MSSubClass + MSZoning +
        LotArea + LotShape + LandContour +
        Neighborhood + Condition1 +
        BldgType + HouseStyle + OverallQual + OverallCond +
        YearBuilt +
        YearRemodAdd + RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + Foundation + BsmtFinSF1 +
        BsmtUnfSF + TotalBsmtSF + HeatingQC + CentralAir +
        GrLivArea + BsmtFullBath +
        FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Fireplaces + GarageType +
        GarageCars + GarageArea + PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + ScreenPorch + MoSold +
        SaleType + SaleCondition + Var_1stFlrSF + Var_2ndFlrSF + Alley,
    data = boston %>%
        rename_at(
            .vars = c("1stFlrSF", "2ndFlrSF", "3SsnPorch"),
            .funs = ~ paste0("Var_", .)
        ),
    importance = "permutation",
    max.depth = 50
)

importance(m4) %>%
    enframe() %>% 
    arrange(desc(value))

test_res4 <- boston_test %>%
    rename_at(
        .vars = c("1stFlrSF", "2ndFlrSF", "3SsnPorch"),
        .funs = ~ paste0("Var_", .)
    ) %>%
    filter(!RoofMatl %in% c("ClyTile", "Metal"), !HeatingQC %in% "Po") %>%
    mutate(
        SalePrice_pred = predict(m4, .)$predictions,
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred
    )


# Mean err plot
test_res4 %>%
    ggplot() +
    aes(x = err) +
    geom_histogram() +
    geom_vline(xintercept = 0)

# Mean err plot
test_res4 %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

# err sd plot
test_res4 %>%
    ggplot() +
    aes(y = sqrt(abs(err)), x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

1 - var(test_res4$err, na.rm = TRUE) / var(test_res4$err_base)
```

# Back go Gamma GLM

Given all of the above, there appear to not be enough irregularities in the
GLM (non-linearities, interactions, etc), for other methods to outperform it.
There was however, a purely practical matter of having trouble with some
rare factor levels. 

I solve this with, ... mixed effects model, using a GAM, because it's faster
than a full bayesian treatment. The GAM model is same as GLM model above,
except it uses thin plate smoothing, and a random effect for `HeatingQC`.

Upon closer examination `RoofMatl` nearly constant.

```{r}
library(mgcv)

m5 <- gam(
    SalePrice ~ MSSubClass + MSZoning +
        s(LotArea, k = 5) + LotShape + LandContour + LotConfig + LandSlope +
        Neighborhood + Condition1 + Condition2 + BldgType + HouseStyle +
        s(OverallQual, k = 10) + s(OverallCond, k = 5) + s(YearBuilt, k = 10) + s(YearRemodAdd, k = 10) +
        RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + ExterCond + Foundation + BsmtFinSF1 + BsmtFinSF2 +
        BsmtUnfSF + s(TotalBsmtSF, k = 10) + Heating + CentralAir
        + LowQualFinSF + s(GrLivArea, k = 10) + BsmtFullBath
        + BsmtHalfBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageType +
        s(GarageCars, k = 4) + s(GarageArea, k = 10) + PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + ScreenPorch + PoolArea + s(MoSold, k = 5) +
        YrSold + SaleType + SaleCondition + Alley + s(HeatingQC, bs = "re") +
        s(var_1stFlrSF, k = 10) + s(var_2ndFlrSF, k = 10) + var_3SsnPorch,
    Gamma(link = log),
    data = boston %>%
        mutate(across(HeatingQC, as.factor)) %>%
        rename_with(
            \(x) {
                if_else(
                    str_detect(x, "^[0-9]"),
                    paste0("var_", x),
                    x
                )
            }
        ),
    select = TRUE
)

summary(m5)

test_res5 <- boston_test %>%
    mutate(across(HeatingQC, as.factor)) %>%
    rename_with(
        \(x) {
            if_else(
                str_detect(x, "^[0-9]"),
                paste0("var_", x),
                x
            )
        }
    ) %>%
    mutate(
        SalePrice_pred = predict(m5, ., type = "response"),
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred
    )

1 - var(test_res5$err, na.rm = TRUE) / var(test_res5$err_base)
test_res5$err %>% sd()
test_res5$err_base %>% sd()
test_res5$err %>% summary()
test_res5$err_base %>% summary()

# Mean err plot
test_res5 %>%
    ggplot() +
    aes(x = err) +
    geom_histogram() +
    geom_vline(xintercept = 0)

# Mean err plot
test_res5 %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

# err sd plot
test_res5 %>%
    ggplot() +
    aes(y = sqrt(abs(err)), x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)
```

# Summary

```{r}
tribble(
    ~model, ~rsq,
    "Gamma GLM, with splines", 1 - var(test_res$err) / var(test_res$err_base),
    "LASSO (Same as GLM otherwise)",  1 - var(test_res2$err) / var(test_res2$err_base),
    "Rpart",  1 - var(test_res3$err) / var(test_res3$err_base),
    "Forest", 1 - var(test_res4$err) / var(test_res4$err_base),
    "GAM", 1 - var(test_res5$err) / var(test_res5$err_base),
)

bind_rows(
    glm = test_res,
    lasso = test_res2,
    rpart = test_res3,
    forest = test_res4,
    gam = test_res5,
    .id = "model"
) %>% 
    filter(SalePrice_pred < max(boston$SalePrice)) %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred, group = model, color = model) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)
```

# Predictions

At the end of the day GLM seems to de the best.

```{r}
test_test_res <- boston_test_test %>%
    filter(
        # !RoofMatl %in% c("ClyTile", "Metal", "Roll"),
        !RoofMatl %in% c("Roll"),
        # !HeatingQC %in% c("Po"),
        !Heating %in% c("OthW")
    ) %>%
    mutate(
        SalePrice_pred = predict(m1, ., type = "response"),
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred
    )
boston_test_test %>%
    slice(attr(test_test_res$SalePrice_pred, "non-estim"))
1 - var(test_test_res$err, na.rm = TRUE) / var(test_test_res$err_base)
test_test_res$err %>% sd()
test_test_res$err_base %>% sd()
test_test_res$err %>% summary()
test_test_res$err_base %>% summary()

# Mean err plot
test_test_res %>%
    ggplot() +
    aes(x = err) +
    geom_histogram() +
    geom_vline(xintercept = 0)

# Mean err plot
test_test_res %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

# err sd plot
test_test_res %>%
    ggplot() +
    aes(y = sqrt(abs(err)), x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)
```

# Submission

```{r}
library(mice)

boston_submission <- unz(
    data_zip,
    "test.csv"
) %>%
    read_boston() %>%
    mutate_boston()

boston_submission %>%
    select(all_of(all.vars(update(formula(m1), NULL ~ .)))) %>%
    summarize(across(everything(), \(x) mean(is.na(x)))) %>%
    pivot_longer(everything()) %>%
    filter(value > 0) %>%
    arrange(desc(value))

boston_submission_imp <- boston_submission %>%
    mutate(across(where(is.character), as.factor)) %>%
    select(all_of(all.vars(update(formula(m1), NULL ~ .)))) %>%
    rename_with(
        \(x) { if_else( str_detect(x, "^[0-9]"), paste0("var_", x), x) }
    ) %>%
    mice(method = "rf", m = 1) 

boston_submission_complete <- complete(boston_submission_imp) %>%
    rename_with( \(x) { str_remove(x, "^var_") }) %>%
    as_tibble()

boston_submission_complete %>%
    mutate(
        Id = boston_submission$Id,
        SalePrice = predict(m1, ., type = "response"),
    ) %>%
    select(Id, SalePrice) %>%
    write_csv(str_glue("submission_{format(today(), '%F')}.csv"))
```

# After first submission

So I looked into other's notebooks to see if I am missing something.
The main difference I did notice is removing outliers. Other than that, people
usually use a much shorter list of variables. so maybe some parsimony is in
order.

Notably I did not see people use complicated encodings for the dummy variables.

# Parsimony

Before getting to outliers let's identify the variables of intrest. I use the
top 15 variables with highest importance rating from the random forest.

Among these I look for outliers. (The plot is best viewed on a large screen,
or with zoom).

```{r}
top15 <- importance(m4) %>%
    enframe() %>% 
    arrange(desc(value)) %>%
    mutate(p = value / sum(value)) %>%
    filter(p > 0.01) %>%
    pull(name) %>%
    str_remove("^Var_")

boston %>%
    mutate(
        #infl = influence(m1)$hat,
        infl = NA,
        outlier = if_else(
            SalePrice > 6e5 | `1stFlrSF` > 2500 |
                TotalBsmtSF > 3000 | LotArea > 50e3,
            #infl >= quantile(infl, 0.99),
            Id,
            NA
        ),
    ) %>%
    select(all_of(top15), SalePrice, outlier, infl) %>%
    select(SalePrice, where(is.numeric), outlier, infl) %>%
    pivot_longer(cols = any_of(top15)) %>%
    ggplot() +
    aes(
        x = SalePrice,
        y = value,
        label = scales::percent(outlier)
    ) +
    geom_point() +
    geom_point(
        data = boston_test %>%
            filter(Id == 1299) %>%
            mutate(outlier = Id, infl = NA) %>%
            select(all_of(top15), SalePrice, outlier, infl) %>%
            select(SalePrice, where(is.numeric), outlier, infl) %>%
            pivot_longer(cols = any_of(top15)),
        color = "red", size = 2
    ) +
    geom_text(na.rm = TRUE, hjust = -0.3) +
    facet_wrap(vars(name), scale = "free_y")
```

With that in mind I apply essentially the same model as before, this time I put
splines everywhere.


```{R}
m6 <- glm(
    SalePrice ~ MSSubClass + MSZoning +
        ns(LotArea, 5) + LotShape + LandContour +
        LotConfig + LandSlope + Neighborhood + Condition1 + Condition2 +
        BldgType + HouseStyle + ns(OverallQual, 5) + ns(OverallCond, 3) +
        ns(YearBuilt, 5) +
        YearRemodAdd + RoofStyle + Exterior1st + Exterior2nd +
        ExterQual + ExterCond + Foundation + BsmtFinSF1 + BsmtFinSF2 +
        BsmtUnfSF + TotalBsmtSF + Heating + HeatingQC + CentralAir +
        `1stFlrSF` + `2ndFlrSF` + LowQualFinSF +
        ns(GrLivArea, 5) + BsmtFullBath +
        BsmtHalfBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr +
        KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageType +
        GarageCars + ns(GarageArea, 5) +
        PavedDrive + WoodDeckSF + OpenPorchSF +
        EnclosedPorch + `3SsnPorch` + ScreenPorch + PoolArea + ns(MoSold, 5) +
        YrSold + SaleType + SaleCondition + Alley,

    # SalePrice ~ ns(OverallQual, 3) + ns(log(GrLivArea + 1), 5) + ns(log(TotalBsmtSF + 1), 5) +
    # ns(YearBuilt, 5) + ns(log(`1stFlrSF` + 1), 5) + ns(GarageCars, 5) + ns(GarageArea,
    # 5) + ExterQual + ns(YearRemodAdd, 5) + KitchenQual +
    # ns(log(`2ndFlrSF` + 1), 5) + ns(FullBath, 5) + ns(BsmtFinSF1, 5) + ns(TotRmsAbvGrd, 5) +
    # ns(log(LotArea + 1), 5) + 
    # TotRmsAbvGrd + Neighborhood + Fireplaces + GarageType + HeatingQC +
    # Foundation + HouseStyle,


    # SalePrice ~ OverallQual + GrLivArea + TotalBsmtSF +
    # YearBuilt + `1stFlrSF` + GarageCars + GarageArea + ExterQual +
    # YearRemodAdd + KitchenQual + `2ndFlrSF` + FullBath + BsmtFinSF1 +
    # TotRmsAbvGrd + LotArea,

    Gamma(link = log),
    data = boston,
    #subset = !()
)

summary(m6)
```

```{r}
test_res6 <- boston_test %>%
    filter(!outlier) %>%
    #filter(!RoofMatl %in% c("ClyTile", "Metal"), !HeatingQC %in% "Po") %>%
    # select(Id, SalePrice, all_of(top15)) %>%
    mutate(
        SalePrice_pred = predict(m6, ., type = "response"),
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred,
        .before = everything()
    ) 

1 - var(test_res6$err) / var(test_res6$err_base)
test_res6$err %>% sd()
test_res6$err_base %>% sd()
test_res6$err %>% summary()
test_res6$err_base %>% summary()

# Mean err plot
test_res6 %>%
    ggplot() +
    aes(x = err) +
    geom_histogram() +
    geom_vline(xintercept = 0)

# Mean err plot
test_res6 %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

# err sd plot
test_res6 %>%
    ggplot() +
    aes(y = sqrt(abs(err)), x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)
```


```{R}
m7 <- ranger(
    SalePrice ~ OverallQual + GrLivArea + TotalBsmtSF +
        YearBuilt + Var_1stFlrSF + GarageCars + GarageArea + ExterQual +
        YearRemodAdd + KitchenQual + Var_2ndFlrSF + FullBath + BsmtFinSF1 +
        TotRmsAbvGrd + LotArea,
    data = boston %>%
        rename_at(
            .vars = c("1stFlrSF", "2ndFlrSF", "3SsnPorch"),
            .funs = ~ paste0("Var_", .)
        )
)

summary(m7)
```

```{r}
test_res6 <- boston_test %>%
    filter(!outlier) %>%
    # select(Id, SalePrice, all_of(top15)) %>%
    mutate(
        SalePrice_pred = predict(m6, ., type = "response"),
        err_base = SalePrice - mean(boston$SalePrice),
        err = SalePrice - SalePrice_pred,
        .before = everything()
    ) 

1 - var(test_res6$err) / var(test_res6$err_base)
test_res6$err %>% sd()
test_res6$err_base %>% sd()
test_res6$err %>% summary()
test_res6$err_base %>% summary()

# Mean err plot
test_res6 %>%
    ggplot() +
    aes(x = err) +
    geom_histogram() +
    geom_vline(xintercept = 0)

# Mean err plot
test_res6 %>%
    ggplot() +
    aes(y = err, x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)

# err sd plot
test_res6 %>%
    ggplot() +
    aes(y = sqrt(abs(err)), x = SalePrice_pred) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0)
```


# Outliers

```{r}
```